### 2020-08-03 confirm-activity/tex/confirm-availability.tex
fix intro and reorganize the paper
more reorganizing

\section{Confirm Availability}
In this section, we present a solution for confirming availability of 
Ursulas. As mentioned before, in the early operation stage of the network we only 
require Ursulas to be online and responsive to the re-encryption 
requests issued by Bob.

@@

\subsection{Optimistic Challenge-based Approach}
The proposed solution is centered around two important concepts: requiring minimal 
changes to the current network implementation, and minimizing the additional overhead. \\

\noindent{\bf Discovering Working Ursulas.} Recall that in the NuCypher network, Bob receives a map from Alice containing 
the set of Ursulas that has the key fragments needed to implement the access control policy. 
When issuing a re-encryption request, Bob uses this map (in association with the network discovery protocol) to reach each of these Ursulas and obtain 
the service.

@@

The discovery process also includes retrieving the keypair a working Ursula uses for the re-encryption service purposes. We call this keypair a stamp, and we require an Ursula to use her stamp when signing all messages related to the proposed confirm availability protocol. \\

\noindent{\bf Optimistic Ursula Challenging.} Once Bob discovers the working Ursulas listed in the policy map, he can connect with each of them and start issuing service requests. As noted, this communication is one-to-one meaning that no other Ursulas (or any 
NuCypher network participant) mediates the communication between Bob and working  
Ursula. This in turn means that no one can attest to whether Ursula has responded if Bob 
complains later that he was not served.

The main idea is to add a mediator, or potentially a witness, in the service process (if needed) to monitor a specific working Ursula and challenge its responsiveness. Hence, it is an optimistic protocol invoked only when Bob complains about not receiving the service. In detail, for each round (where a 
round is the time needed to mine a block or several blocks on the blockchain) a set of Ursulas is selected at random. We call these gateway Ursulas. Bob contacts a working Ursula asking for the re-encryption service as usual. 
If this Ursula does not respond, Bob complains to a gateway about it. At this point, the gateway will act as an intermediary and forwards Bob's request to this working Ursula on behalf of Bob and waits for the answer. If no answer is received, this gateway will trigger other gateways to perform the same process, i.e., forward the request on behalf of Bob and wait for an answer. If the working 
Ursula is still unresponsive, these gateways will collectively sign a proof-of-unavailability, which is basically a statement saying that the working Ursula was contacted by these gateways and she did not respond, and publish it through the \stakeescrow contract (see Section~\ref{cosi} for an overview of collective signing). Once the proof-of-unavailability is verified, part of the working Ursula's stake will be slashed as a punishment. \\

\noindent{\bf Gateways Selection.} For each round a set of $n$ gateways Ursulas will be selected. A proof-of-unavailability will be accepted by the network if it is signed by at least $t$ gateways among this set (this threshold is a relaxation of requiring all gateways to sign since it could be the case that not all of them are active).

@@

As for the high entropy source of randomness, there are several potential approaches here. We can rely on an external source, e.g., the NIST random beacon~\cite{nist-beacon} or even a combination of multiple sources, for that. Or we can work also in the random oracle model and assume that block hashes are drawn from a uniform distribution, and thus, use the block hash as a random beacon. In particular, for the current round, the hash of the block that was mined $y$ rounds ago is used ($y$ is the confirmation interval in the underlying cryptocurrency system). Alternatively, and to avoid the random oracle assumption, we can use randomness extractors to produce a high entropy beacon from the block hashes which itself could be low entropy~\cite{bonneau2015bitcoin}. \\

\noindent{\bf Proof-of-unavailability processing.} As mentioned previously, a proof-of-unavailability against a working Ursula is a statement stating that this Ursula was unavailable during a specific round signed by at least $t$ gateways out of the $n$ gateways selected for that round. Such a proof is submitted to the \stakeescrow contract and is verified as follows:
\begin{itemize}
\item Produce the list of gateways selected for the current round. This is done by using the same process described previously.

@@

Note that the above assumes that the \stakeescrow contract is aware of the gateways' stamps (or keys) that are used in signing the proof-of-unavailability. This can be done by either expanding the staker list in the contract to contain not only the Ethereum addresses of working Ursulas, but also their stamps. Another option is to piggyback the stamps (signed by using the key corresponding to the working Ursula's Ethereum address) with the proof-of-unavailability. A more simpler, and efficient, option is to sign the proof-of-unavailability by using the key corresponding to the working Ursula's Ethereum address in the first place, and thus, the \stakeescrow contract will not need an additional information. Which option to use depends merely on efficiency considerations. \\

\noindent{\bf Quantifying the Financial Punishment or Slashing Value.}
A question that comes to mind is how much should be revoked from Ursula's stake once a proof-of-unavailability is approved? Quantifying this amount should be driven by two factors; the unavailability duration and the utility gain (or profits) of this cheating behavior in terms of the collected fees and inflation rewards for that duration.

Accordingly, we can compute this value to be equal to the fees and inflation rewards that an Ursula is supposed to receive in a round (recall that a round is the time needed to mine a block or several blocks on the blockchain). Hence, the working Ursula will, first, lose her fees and inflation rewards from the network, and second, lose the same amount from her stake. Such a loss will take place even if a single proof-of-unavailability is received against a working Ursula within a round. In fact, the \stakeescrow contract will process only one proof against a working Ursula per round to reduce computational costs in the system. \\

\noindent{\bf Working Only During the Challenge Phase.}
A potential issue under the proposed optimistic scheme is that a working Ursula may operate only during the challenge phase. That is, she ignores any fresh request coming from Bob, and just replies afterwards when receiving the same request again (i.e., when it is forwarded by the gateways during the challenge phase).

We argue that such a behavior is not a practical issue since a rational Ursula will be online eitherway to monitor whether this is a challenge phase or not, and that the amount of work needed to respond to a re-encryption request is minimal. Hence, there is no incentive at all to follow this strategy, meaning that a rational Ursula will act honestly. \\

\noindent{\bf DoS Attacks.} 
Another potential issue is exploiting the unavailability complaints to perform a DoS attack against the gateways and working Ursulas. In detail, Bob may lie and issue complaints against working Ursulas even though they are responsive just to slash their stakes. Or an attacker may replay these complaints, or issue them on behalf of Bob, to slash a working Ursula. Or the goal could be to overwhelm the gateways with the challenge process and make them unavailable to perform the re-encryption service (recall that the gateways are originally working Ursulas in the NuCypher network).

@@

\noindent{\bf Unresponsive Gateways.}
A third issue that we may encounter in the proposed solution is that the gateways themselves could be unresponsive. This will stall the challenge phase and make it infeasible to prove that some working Ursula is unavailable. We believe that such an issue will be organically handled by the network. That is, the larger the number of Ursulas in the network, the higher the chances of having more honest Ursulas. By increasing the number of selected gateways $n$, and given that the selection process is random, the chances of having at least $t$ honest gateways in a round will be high.

>>>>

\section{Confirm Availability Solution}
\label{confirm-availability}
In this section, we present a solution for confirming availability of Ursulas. As mentioned before, in the early operation stage of the network we only require Ursulas to be online and responsive to the re-encryption 
requests issued by Bob.

The proposed solution is called \emph{Optimistic Challenge-based Approach}, which is centered around two important concepts: requiring minimal changes to the current network implementation, and minimizing the additional overhead.

@@

\paragraph{\bf Discovering working Ursulas.} 
Recall that in the NuCypher network, Bob receives a map from Alice containing 
the set of Ursulas that has the key fragments needed to implement the access control policy. 
When issuing a re-encryption request, Bob uses this map (in association with the network discovery protocol) to reach each of these Ursulas and obtain 
the service.

@@

The discovery process also includes retrieving the keypair a working Ursula uses for the re-encryption service purposes. We call this keypair a stamp, and we require an Ursula to use her stamp when signing all messages related to the proposed confirm availability protocol.

\paragraph{\bf Optimistic Ursula challenging.} 
Once Bob discovers the working Ursulas listed in the policy map, he can connect with each of them and start issuing service requests. As noted, this communication is one-to-one meaning that no other Ursulas (or any 
NuCypher network participant) mediates the communication between Bob and working  
Ursula. This in turn means that no one can attest to whether Ursula has responded if Bob 
complains later that he was not served.

The main idea is to add a mediator, or potentially a witness, in the service process (if needed) to monitor a specific working Ursula and challenge its responsiveness. Hence, it is an optimistic protocol invoked only when Bob complains about not receiving the service. In detail, for each round (where a 
round is the time needed to mine a block or several blocks on the blockchain) a set of Ursulas is selected at random. We call these gateway Ursulas. Bob contacts a working Ursula asking for the re-encryption service as usual. If this Ursula does not respond, Bob complains to a gateway about it. At this point, the gateway will act as an intermediary and forwards Bob's request to this working Ursula on behalf of Bob and waits for the answer. If no answer is received, this gateway will trigger other gateways to perform the same process, i.e., forward the request on behalf of Bob and wait for an answer. If the working 
Ursula is still unresponsive, these gateways will collectively sign a proof-of-unavailability, which is basically a statement saying that the working Ursula was contacted by these gateways and she did not respond, and publish it through the \stakeescrow contract (see Section~\ref{cosi} for an overview of collective signing). Once the proof-of-unavailability is verified, part of the working Ursula's stake will be slashed as a punishment.

\paragraph{\bf Gateways Selection.} 
For each round a set of $n$ gateways Ursulas will be selected. A proof-of-unavailability will be accepted by the network if it is signed by at least $t$ gateways among this set (this threshold is a relaxation of requiring all gateways to sign since it could be the case that not all of them are active).

@@

As for the high entropy source of randomness, there are several potential approaches here. We can rely on an external source, e.g., the NIST random beacon~\cite{nist-beacon} or even a combination of multiple sources, for that. Or we can work also in the random oracle model and assume that block hashes are drawn from a uniform distribution, and thus, use the block hash as a random beacon. In particular, for the current round, the hash of the block that was mined $y$ rounds ago is used ($y$ is the confirmation interval in the underlying cryptocurrency system). Alternatively, and to avoid the random oracle assumption, we can use randomness extractors to produce a high entropy beacon from the block hashes which itself could be low entropy~\cite{bonneau2015bitcoin}.

\paragraph{\bf Proof-of-unavailability processing.} 
As mentioned previously, a proof-of-unavailability against a working Ursula is a statement stating that this Ursula was unavailable during a specific round signed by at least $t$ gateways out of the $n$ gateways selected for that round. Such a proof is submitted to the \stakeescrow contract and is verified as follows:
\begin{itemize}
\item Produce the list of gateways selected for the current round. This is done by using the same process described previously.

@@

Note that the above assumes that the \stakeescrow contract is aware of the gateways' stamps (or keys) that are used in signing the proof-of-unavailability. This can be done by either expanding the staker list in the contract to contain not only the Ethereum addresses of working Ursulas, but also their stamps. Another option is to piggyback the stamps (signed by using the key corresponding to the working Ursula's Ethereum address) with the proof-of-unavailability. A more simpler, and efficient, option is to sign the proof-of-unavailability by using the key corresponding to the working Ursula's Ethereum address in the first place, and thus, the \stakeescrow contract will not need an additional information. Which option to use depends merely on efficiency considerations.

\paragraph{\bf Quantifying the Financial Punishment or Slashing Value.}
A question that comes to mind is how much should be revoked from Ursula's stake once a proof-of-unavailability is approved? Quantifying this amount should be driven by two factors; the unavailability duration and the utility gain (or profits) of this cheating behavior in terms of the collected fees and inflation rewards for that duration.

Accordingly, we can compute this value to be equal to the fees and inflation rewards that an Ursula is supposed to receive in a round (recall that a round is the time needed to mine a block or several blocks on the blockchain). Hence, the working Ursula will, first, lose her fees and inflation rewards from the network, and second, lose the same amount from her stake. Such a loss will take place even if a single proof-of-unavailability is received against a working Ursula within a round. In fact, the \stakeescrow contract will process only one proof against a working Ursula per round to reduce computational costs in the system.

\paragraph{\bf Working Only During the Challenge Phase.}
A potential issue under the proposed optimistic scheme is that a working Ursula may operate only during the challenge phase. That is, she ignores any fresh request coming from Bob, and just replies afterwards when receiving the same request again (i.e., when it is forwarded by the gateways during the challenge phase).

We argue that such a behavior is not a practical issue since a rational Ursula will be online eitherway to monitor whether this is a challenge phase or not, and that the amount of work needed to respond to a re-encryption request is minimal. Hence, there is no incentive at all to follow this strategy, meaning that a rational Ursula will act honestly.

\paragraph{\bf DoS Attacks.} 
Another potential issue is exploiting the unavailability complaints to perform a DoS attack against the gateways and working Ursulas. In detail, Bob may lie and issue complaints against working Ursulas even though they are responsive just to slash their stakes. Or an attacker may replay these complaints, or issue them on behalf of Bob, to slash a working Ursula. Or the goal could be to overwhelm the gateways with the challenge process and make them unavailable to perform the re-encryption service (recall that the gateways are originally working Ursulas in the NuCypher network).

@@

\paragraph{\bf Unresponsive Gateways.}
A third issue that we may encounter in the proposed solution is that the gateways themselves could be unresponsive. This will stall the challenge phase and make it infeasible to prove that some working Ursula is unavailable. We believe that such an issue will be organically handled by the network. That is, the larger the number of Ursulas in the network, the higher the chances of having more honest Ursulas. By increasing the number of selected gateways $n$, and given that the selection process is random, the chances of having at least $t$ honest gateways in a round will be high.

### 2020-08-03 confirm-activity/tex/confirm-service-activity.tex
more reorganizing

\section{Confirm Service Activity}
\label{confirm-service-activity}
In this section, we present potential solutions for the confirm service activity 
problem. The goal is to come up with provably secure solutions that allows an 
Ursula to prove that it has served a given number of distinct re-encryption 
requests within a given period.

@@

\subsection{Potential Solutions}
\label{solutions}
This section outlines several potential solutions for how to let Ursula prove 
that she served a given number of distinct requests in a publicly verifiable way. 
One of these solutions, the PCD-based one, is still a work in progress. The goal 
is to share the high-level idea of each of these solutions and to chose the best one,
after we define the meaning of best, to be adopted by the NuCypher network.

\subsubsection{PCD-based Scheme.}
The main idea here is to adapt the PCD framework so that Ursula
can combine the correctness proofs she computes for Bobs' requests in a single proof 
attesting to the following fact: ``Ursula has served $\omega$ distinct re-encryption 
requests correctly."

@@

\subsubsection{CoSi-based Scheme.}
This solution utilizes the idea of collective signing by electing a committee 
that will sign a report submitted by a specific Ursula after verifying that 
the report supports the claim that ``Ursula has served $\omega$ distinct 
re-encryption requests correctly."

@@

\subsubsection{Commit/Challenge/Open-based Scheme.}
This solution utilizes the idea of commit/challenge/open protocols. 
In details, Ursula keeps track of the requests coming from Bob(s) 
during a time round and assign each of them a unique sequence 
number. That is, Ursula replies with $cFrag$ and the correctness proof 
along with a sequence number showing the order of the request within 
the batch of requests handled during a round. At the end of the round, 
Ursula constructs a Merkle tree of all requests, where 
the requests (and their replies) are the leaves of the tree ordered by the sequence
numbers. Ursula signs the root of the tree, denoted as $root$ to produce 
a signature $\sigma_{root}$, then it publishes $(\omega, root, \sigma_{root})$ 
to the network (recall that $\omega$ is the number of served requests).

>>>>

\section{Confirm Service Activity Solutions}
\label{confirm-service-activity}
In this section, we present potential solutions for the confirm service activity 
problem. The goal is to come up with provably secure solutions that allows an 
Ursula to prove that it has served a given number of distinct re-encryption 
requests within a given period.

@@

\subsection{PCD-based Scheme.}
The main idea here is to adapt the PCD framework so that Ursula
can combine the correctness proofs she computes for Bobs' requests in a single proof 
attesting to the following fact: ``Ursula has served $\omega$ distinct re-encryption 
requests correctly."

@@

\subsection{CoSi-based Scheme.}
This solution utilizes the idea of collective signing by electing a committee 
that will sign a report submitted by a specific Ursula after verifying that 
the report supports the claim that ``Ursula has served $\omega$ distinct 
re-encryption requests correctly."

@@

\subsection{Commit/Challenge/Open-based Scheme.}
This solution utilizes the idea of commit/challenge/open protocols. 
In details, Ursula keeps track of the requests coming from Bob(s) 
during a time round and assign each of them a unique sequence 
number. That is, Ursula replies with $cFrag$ and the correctness proof 
along with a sequence number showing the order of the request within 
the batch of requests handled during a round. At the end of the round, 
Ursula constructs a Merkle tree of all requests, where 
the requests (and their replies) are the leaves of the tree ordered by the sequence
numbers. Ursula signs the root of the tree, denoted as $root$ to produce 
a signature $\sigma_{root}$, then it publishes $(\omega, root, \sigma_{root})$ 
to the network (recall that $\omega$ is the number of served requests).
